Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-05-08 Tex/elsevier/trindade_solar_energy_rev0.tex
updated paper text

%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar photovoltaic (PV) systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}. However, this growth is not driven by isolated systems.

In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, Saber, or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
%
%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
%
%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth. In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials. SPV...
%
%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization). Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.  
%
%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution. 
%
%PV systems can be classified into grid-connected and stand-alone systems. At this proposal, only off-grid or stand-alone systems will be considered. The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.  
However, those tools are based on running experiments in simulation models. Simulation has the advantage of being cheap (if compared to test in real systems) and can be employed before the system design is concluded but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

@@

In prior studies, the evaluation of PV systems w.r.t. user requirements were performed by simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}. Related to formal methods, studies were carried out toward the modeling of power smart grids~\cite{Akram2018} and solar panels~\cite{Driouich2017}; however, those studies do not perform automated verification. 
%
In addition, recent research performed a formal study of PV farms, where the focus has been the interaction with the grid~\cite{Abate2017}; or to model a PV system and to verify the maximum power point of solar panels with the use of Jmodelica tool~\cite{Driouich2018}. Both studies restrict to PV panels, and do not include batteries, inverters, and charge controllers.

%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t
This paper makes three original contributions. % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly
Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system. Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approaches based on simulation.

%\textcolor{red}{This introduction is missing the description of the vision, approach and results. In particular, try to match each paragraph to: problem, vision, approach, results and contributions.} 
%
%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.

\textit{Outline}. Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling. Section~\ref{sec:AutomatedVerification} presents the automated verification technique. Section~\ref{sec:sizingcheck} shows how to perform the sizing of a stand-alone PV system. The methodology is presented in section~\ref{sec:Methodology}. Section~\ref{sec:results} is devoted to the results. Section~\ref{sec:Conclusions} presents the conclusion and describes future work.

%--------------------------------------------------------
\section{Solar Photovoltaic System }
\label{sec:SolarPhotovoltaicSystem}
%--------------------------------------------------------
%
%According to \cite{Roy}, a 
%A PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time. 
%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
%For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}. 
%
PV systems are classified into distinct types~\cite{Mohanty}. %: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system. %, where another source(s) of energy can work together with the solar PV. % system to provide the required demand.
%, such as wind, biomass or diesel, 
%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
%
%\begin{itemize}
%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
%\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
%\end{itemize}
Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, 
%stand-alone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%stand-alone systems 
%can be split into several categories. However, 
the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of this study.
%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
%PV array, battery, MPPT and AC load. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}. Because of the AC load, an inverter (DC to AC converter) is required. 
%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.

@@

\subsection{Design and Simulation of Solar PV systems}
The design and validation of a PV system can be done by hand or with the aid of a software tool. The PV sizing can be done using different methods, and here we reference the critical period as an effective one~\cite{Pinho}.
%
%In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
% to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice. 
This section we evaluated the most popular tools available in the literature and summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.

@@

As highlights, only Hybrid2 does not have technical support; HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 

@@

\begin{table}[!t]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Comparative coverage of reference software}
\label{table:softwares}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{c | c | c | c | c | c}
\hline
\hline
Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen} & \rotatebox{90}{Hybrid2}\\
\hline
\hline
Support & X & X & X & X &  \\
\hline
Off-grid systems &   &   & X & X & X\\
\hline
Hybrid systems &  &  & X & X & X\\
\hline
Photovoltaics & X & X & X & X & X\\
\hline
Batteries &  &  & X &  & X\\
\hline
\makecell{Main technical (T) \\ or economical(E)} & T & T & E & E & T \\
\hline
Optimization &  &  & X & X &  \\
\hline
Sensitive analysis &  &  & X & X & \\
\hline
\hline
\end{tabular}
\end{table}

@@

\subsection{PV system model}

@@

\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$) %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions 
(provided by PV manufacturers). $ I_{ph,ref} $ can be approximated to the reference short-circuit current \cite{Villalva} that is provided by PV manufacturers ($ I_{sc,ref} $).
%\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
%%
The cell temperature ($ T $) in degree Celsius is described by ~\ref{eq:Tcell}~\cite{Ross}:
\begin{equation}
\label{eq:Tcell}
T = T_{air} + \dfrac{NOCT-20}{800}G,
\end{equation}

\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C) that is found at the PV manufacturer's data-sheet \cite{Ross}, and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.

@@

%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}. This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
%
%\begin{equation}
%\label{eq:CC10}
%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
%\end{equation}
%
%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
%
\begin{multline}
\label{eq:Vcbat}
V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
\end{multline}

Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period. %; however, during recharge it is much more difficult \cite{Copetti}.

@@

The \textbf{charge controller} or controller is a set of items (DC-DC converter, MPPT, and switches) and can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. MPPT, or maximum power point tracking, is the electronic control mechanism mostly used nowadays and that maintains the PV operating at the voltage of maximum power. Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 
%
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%
%
%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components. The use of battery as a storage form implies thus the presence of a charge controller. 
%
%%%%%%%%%%In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values. 
%
%The controller allows the management of energy between the load and the battery \cite{Mellit}. 
%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $). The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).

@@

%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model). 
%
%
%--------------------------------------------------
\subsection{Availability of Stand-alone PV Systems}
\label{sec:availability}
%--------------------------------------------------
Each stand-alone PV system, like any other power systems, has a specific level of availability. This reliability level impacts various issues, as system performance, production, feasibility, and investment. The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}. The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.

The system availability definition depends on how critical the load application is. For critical loads, 99\% is considered acceptable. While in a ordinary house electrical load, 95\% is considered acceptable. As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system. An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.

With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong. It is important to evaluate how critical the load application is and the horizon of evaluation. However this analysis can be useful, for example, to improve the sized battery autonomy.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.

@@

checking. In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}. %CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing. For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs. \textcolor{red}{It is unclear what a CPA is.}

@@

The flowchart of the proposed automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.

>>>>

%The definition of energy access usually includes both electricity access and access to modern fuels for cooking and heating, in order to replace traditional biomass. 
%Increased access to energy allows economic growth and poverty alleviation \cite{Karekesi}. 
%
%Among the options of renewable sources, there are hydro, wind, and solar photovoltaic (PV). 
Only a niche market a few years ago, solar PV systems are now becoming a mainstream electricity provider, with an increase of approximately 50\% from 2016 to 2017 in terms of new installations of PV~\cite{EPIA}. %However, this growth is not driven by stand-alone systems.

In order to simulate or evaluate a PV system there are a myriad of specialized tools available in the market, such as RETScreen, HOMER, PVWatts, SAM, and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}; and even general purpose simulation tools such as PSpice, and MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
%
%However, to the best of our knowledge, this work can be the first work to perform automated verification of a stand-alone solar PV project solution.  
%
%According to \cite{SEIA} and \cite{Chauhan}, solar is the most abundant source of renewable energy on earth. In SPV system, solar radiations are captured from the sun and turned into electricity using SPV cells made of silicon and other materials. SPV...
%
%In order to address different aspects of a SPV project, there is a myriad of public domain and commercial software available. According to \cite{Brooks}, the capabilities of these tools range from simple solar resource and energy production estimative, to site survey and system design tools, to complex financial analysis software (with optimization). Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.  
%
%Manufactures and integrators have yet their proprietary software to perform various system sizing, with the drawback of include just their own products among the possibilities of choice, what restrict the solution. 
%
%PV systems can be classified into grid-connected and stand-alone systems. At this proposal, only off-grid or stand-alone systems will be considered. The utilization of solar energy in off-grid mode has the potential to meet the energy need for remote rural areas of developing countries.  
However, those tools are based on running experiments in simulation models. Simulation has the advantage of being cheap (if compared to test in real systems) %and can be employed before the system design is concluded 
but it has the drawback of an incomplete coverage since the verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

@@

In prior studies, the evaluation of PV systems w.r.t. user requirements were performed by simulation tools using MATLAB/Simulink~\cite{Benatiallah2017, Natsheh2012}, or HOMER Pro \cite{Lamnadi2017}. Related to formal methods, in 2015, an approach for applying Monte-Carlo simulation to power system protection schemes presented limitations of incomplete coverage of all possible operating conditions~\cite{Sengupta2015}. The authors proposed an automated simulation-based verification technique to verify correctness of protection settings efficiently using hybrid automata-temporal-logic framework. Other related study from 2015 include a framework named Modana to achieve an integrated process from modeling with SysML/MARTE to analysis with statistical model checking the non-functional properties such as time and energy~\cite{Cheng2015}. In order to demonstrate Modana's capability, the authors modelled energy-aware buildings as a case study, and discussed the analysis on energy consumption in different scenarios. The focus here is on HVAC (heating, ventilation, and air conditioning) systems. In 2017, a researcher suggested the application of formal methods to verify and control the behavior of computational devices interacting over a shared and smart infrastructure~\cite{Abate2017}. The author discussed the aggregation of large populations of thermostatically-controlled loads and of PV panels, and the corresponding problems of energy management in smart buildings, of demand-response on smart grids, and respectively of frequency stabilization and grid robustness. The focus was on controlling the behavior of components, thereby verifying the smart grid as a ``system of systems'' within the context of ``internet of things''. The author used approximate model checking of stochastic and hybrid models. In 2018, a verification methodology was proposed with applications to PV panels and its distributed power point tracking~\cite{Driouich2018}. This approach relied on representing unpredictable behavior of the environment to cover all possible feasible scenarios. The simulation results obtained by JModelica covered the system's complete dynamic behavior; however, it was evident the time consuming issue with almost three days of computer effort to verify the design space of one operation hour of the PV panels behavior. Another work from 2018 was the approach to modeling smart grid components using a formal specification. The authors used a state-based formal specification language named Z; they demonstrated the application of Z to four smart grid components~\cite{Akram2018}. The presented formal specification can be considered as a first step towards modeling of smart grid using formal methods. This approach is based on Petri nets and from the premise that modeling of the smart home leads to clear understanding of the overall behavior of the smart grid.
%%%%%%%%%%%%%
%The experimental results show that the proposed framework is more efficient \textcolor{red}{than what?} in different case studies to find not proper functioning of PV systems than simulation with off-the-shelf tool. 
%This is the first study to apply a formal verification technique to formally check the design of a stand-alone solar PV system. In summary, t

This paper makes three contributions. % Firstly, we describe a modular modeling of each component of a PV system by means of mathematical models that can be encoded into fragments of first-order theories supported by software model checkers. Secondly
Firstly, we propose an algorithm written in language C that implements the automated verification method which formally checks the sizing and the operation of a given stand-alone PV system. Secondly, we evaluate the verification method by comparing three state-of-the-art model checkers in five real case studies. Thirdly, experimental results show that this proposed approach can find subtle design errors in stand-alone PV systems, which are not easily detected by other approach based on simulation.

%\textcolor{red}{This introduction is missing the description of the vision, approach and results. In particular, try to match each paragraph to: problem, vision, approach, results and contributions.} 
%The framework provided at this paper outlines the requirements, the process and the mathematical modeling to perform automated formal verification of a stand-alone PV system, using the satisfiability modulo theories (SMT)-based verification method.
%\textit{Outline}. Section~\ref{sec:SolarPhotovoltaicSystem} gives the background about solar PV systems, design and validation of PV systems, and the mathematical modeling. Section~\ref{sec:AutomatedVerification} presents the automated verification technique. Section~\ref{sec:sizingcheck} shows how to perform the sizing of a stand-alone PV system. The methodology is presented in section~\ref{sec:Methodology}. Section~\ref{sec:results} is devoted to the results. Section~\ref{sec:Conclusions} presents the conclusion and describes future work.
%--------------------------------------------------------
\section{Solar Photovoltaic System }
\label{sec:SolarPhotovoltaicSystem}
%--------------------------------------------------------
%According to \cite{Roy}, a 
%A PV system is designed to give the electric supply to a load. This load can be either Alternate Current (AC) or Direct Current (DC) type. Electric supply can be needed either in daytime or evening time. 
%(in particular cases, in both times). %The most basic PV system can give supply only in daytime.  
%For night hours or rainy days, one needs to hold batteries, where power can be stored and used.% \cite{Gules}. 
PV systems are classified into distinct types~\cite{Mohanty}. %: (1) stand-alone systems, where the energy is generated and consumed in the same place and which do not interact with the main grid; (2) grid-connected systems; and (3) solar PV hybrid system. %, where another source(s) of energy can work together with the solar PV. % system to provide the required demand.
%, such as wind, biomass or diesel, 
%As the goal of this work is just the solutions aimed to isolated/ off-grid application, %therefore it is not considered the on-grid or hybrid configurations.
%\item Stand-alone systems, where the energy is generated and consumed in the same place and which does not interact with the main grid. Normally, the electricity consuming/utilizing device is part of the system, i.e., solar home systems, solar street lighting system, solar lanterns, and solar power plants; 
%\item Grid-connected systems, where the solar PV system is connected to the grid. The grid-connected system can be either a grid-tied system, which can only feed power into the grid and such system cannot deliver power locally during blackouts and emergencies since these systems have to be completely disconnected from the grid and have to be shut down as per national and international electrical safety standards. Some grid-connected PV systems, with energy storage, can also provide power locally in an islanding mode; 
%\item Solar PV hybrid system: In a hybrid system, another source(s) of energy, such as wind, biomass or diesel, can work together with the solar PV system to provide the required demand. In such type of system, main objective is to bring more reliability into the overall system at an affordable way by adding one or more energy sources.
Specifically for remote rural areas of developing countries or places where the grid extension is not feasible, 
%stand-alone systems are one the most used solutions, and 
% depending on the type of load, cost, resources availability, and requirements of the load, 
%stand-alone systems 
%can be split into several categories. However, 
the most suitable configuration is the regulated stand-alone system with battery and AC load; this configuration is the focus of this study.
%, which is the target of this paper, includes PV array, batteries, charge controller, inverter, and AC load.
%PV array, battery, MPPT and AC load. Battery is used to store the extra power of PV system. A charge controller is necessary for this type of system because the useful life of the battery is less than that of the PV module. Extra charging and deep discharging can reduce the battery life \cite{Kim}. Because of the AC load, an inverter (DC to AC converter) is required. 
%This solution has an increase of cost because has more equipment. However, the AC availability brings the advantage of a higher number of AC appliances to use at the houses or consumer units.
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%, which maximizes the transfer of power and avoiding lost at the PV cells \cite{Pinho}. %That resource is found at modern PV systems and is strongly indicated due to its advantages.

@@

\subsection{Sizing and Simulation of Solar PV systems}
The sizing and validation of a PV system can be done by hand or with the aid of tools. Here we reference the critical period~\cite{Pinho} as an effective method to PV sizing.
%
%In order to address different aspects of the PV system design, there are various software tools available in the literature~\cite{Rajanna,Rawat}.
%public domain and commercial software available for the PV market. 
%According to \cite{Brooks}, t
%%%%%%%%%%The capabilities of tools available in the literature range from simple solar resource and energy production estimation, %to site survey and system design tools,
% to complex financial analysis and project optimization. 
%Some tools also provide support to rebate programs applications and tax incentives (specific to each country or region), while other programs and worksheets focus on the technical aspects of system sizing and design.
%
%Manufacturers and integrators have yet their proprietary software to perform inverter string sizing and various system sizing and design tools, with the drawback to just include their own products among the possibilities of choice.

The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.

@@

As highlights, only HOMER and Hybrid2 perform off-grid system with battery backup analysis. %all the tools perform solar photovoltaic analysis; 

@@

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
\caption{Comparative coverage of reference software}
\label{table:softwares}
\begin{tabular}{c | c | c | c | c | c}
\hline
\hline
Characteristic  & \rotatebox{90}{PVWatts} & \rotatebox{90}{SAM} & \rotatebox{90}{HOMER} & \rotatebox{90}{RETScreen} & \rotatebox{90}{Hybrid2}\\
\hline
\hline
Support & X & X & X & X &  \\
\hline
Off-grid systems &   &   & X & X & X\\
\hline
Hybrid systems &  &  & X & X & X\\
\hline
Photovoltaics & X & X & X & X & X\\
\hline
Batteries &  &  & X &  & X\\
\hline
\makecell{Main technical (T) \\ or economical(E)} & T & T & E & E & T \\
\hline
Optimization &  &  & X & X &  \\
\hline
Sensitive analysis &  &  & X & X & \\
\hline
\hline
\end{tabular}
\end{table}

@@

\subsection{PV System Model}

@@

\noindent where the reference state (STC) of the cell is given by the solar irradiance $ G_{ref}=1000 W/m^{2} $ and the temperature $ T_{ref}=298.15 K (=25^{o}C) $; $ \mu_{I} $ is the short-circuit current temperature coefficient ($A/K$); %and corresponds to the photocurrent obtained from a given PV cell working at reference conditions.
$ I_{ph,ref} $ can be approximated to the reference short-circuit current ($ I_{sc,ref} $)\cite{Villalva}.
% that is provided by PV manufacturers ($ I_{sc,ref} $).
%\cite{Jakhrani} that is provided by PV manufacturers ($ I_{sc,ref} $).
%%
The cell temperature ($ T $) in degree Celsius is described by ~\ref{eq:Tcell}~\cite{Ross}:
\begin{equation}
\label{eq:Tcell}
T = T_{air} + \dfrac{NOCT-20}{800}G,
\end{equation}

\noindent where $ T_{air} $ is the ambient temperature, $NOCT$ is the nominal operating cell temperature (in $^{o}$C), and $G$ is the solar irradiance ($ W/m^{2} $) of the place where the PV system is deployed.

@@

%The efficiency of the battery discharge is assumed to be 100\%, according \cite{Copetti}; however, the total amount of useful charge available during discharge is limited by the current rate and temperature given by Equation \ref{eq:CC10}. This equation, called of capacity, is normalized with respect to discharge current corresponding to $ C_{10} $ rated capacity ($ I_{10} $).
%\label{eq:CC10}
%\dfrac{C}{C_{10}} = \dfrac{1.67}{1+0.67 \left( \dfrac{I}{I_{10}} \right)^{0.9} }(1+0.005 %\Delta T)
%Note that when the discharge current tends to zero at 25$^{o}$C, the maximum capacity that can be removed is about 67\% over the capacity.
For the charging process, however, the parameters are described by ~\eqref{eq:Vcbat} as
\begin{multline}
\label{eq:Vcbat}
V_{c} = [2+0.16SOC]+ \dfrac{I}{C_{10}} \left( \dfrac{6}{1+I^{0.86}} + \dfrac{0.48}{(1-SOC)^{1.2}} + 0.036  \right) (1-0.025 \Delta T).
\end{multline}
%Note that SOC can be calculated easily at any point during the discharge period, thereby considering the current drained from batteries during a certain time period. %; however, during recharge it is much more difficult \cite{Copetti}.

@@

The \textbf{charge controller} or controller can be defined as the responsible to manage the energy flow to PV system, batteries and loads by collecting information on the battery voltage and knowing the maximum and minimum values acceptable for the battery voltage. MPPT, or maximum power point tracking, is the electronic control mechanism mostly used nowadays and that maintains the PV operating at the stage of maximum power. %Controllers aim to protect the battery (or batteries) against the excessive charge and discharge \cite{Pinho}, improving its lifetime. 
%
%The resource MPPT, called of maximum power point tracking, is an electronic control mechanism that maintains the PV operating in a voltage that correspond to the voltage of maximum power.
%
%
%As defined by \cite{Hansen} and \cite{Mellit}, all power systems must include a control strategy, which describes the interactions between its components. The use of battery as a storage form implies thus the presence of a charge controller. 
%
%%%%%%%%%%In general, there are two main operating modes for the controller~\cite{Rawat}: normal operating condition, when the battery voltage fluctuates between maximum and minimum voltages; and overcharge or over-discharge conditions, which occur when the battery voltage reaches some critical values. 
%
%The controller allows the management of energy between the load and the battery \cite{Mellit}. 
%The input signals for regulator model are the battery current ($ I_{br} $), PV generator's voltage ($ V_{PV} $), PV generator's current ($ I_{PV} $), and battery voltage ($ V_{b} $). The outputs are battery ($ I_{rb} $) current and used current ($ I_{u} $).

@@

%Therefore, with this equation it is possible to simulate the output power of the inverter, based on information from the inverter's data-sheet and from the DC module or the PV panel that feed the inverter (which are obtained by this study model). 
%
%
%--------------------------------------------------
\subsection{Availability of Stand-alone PV Systems}
\label{sec:availability}
%--------------------------------------------------
%Each stand-alone PV system, like any other power systems, has a specific level of availability. This reliability level impacts various issues, as system performance, production, feasibility, and investment. 
The availability of a stand-alone PV system can be defined as the percentage of time at which a power system is capable of meeting the load requirements~\cite{Khatib2014}. The number of hours that the system is available, divided by 8,760 h, gives the annual system availability.
The system availability definition depends on how critical the load application is. For critical loads, 99\% is considered acceptable. While in a ordinary house electrical load, 95\% is considered acceptable. As an example, a system with 95\% availability is expected to meet the load requirement of 8,322 h during an average year for the entire useful life of the system. An annual availability of 99\% means that the system can operate the load for 8,672 h of the 8,760 h.
%
%With that in mind, it is important to mention that even if a formal verification or a simulation shows that a PV system fails, it doesn't mean that the sizing is wrong. It is important to evaluate how critical the load application is and the horizon of evaluation. However this analysis can be useful, for example, to improve the sized battery autonomy.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Automated Verification Using Model Checking}
\label{sec:AutomatedVerification}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Although simulation and testing explore possible behaviors and scenarios of a given system, they leave open the question of whether unexplored trajectories may contain a flaw~\cite{ClarkeHV18}. Formal verification conducts an exhaustive exploration of all possible behaviors; when a design is said to be ``correct'' by a formal verification method, it implies that all behaviors have been explored; questions regarding adequate coverage or missed behavior becomes irrelevant~\cite{Clarke2012}. Formal verification is a systematic approach that applies mathematical reasoning to obtain guarantees about the correctness of a system; one successful method in this domain is model checking~\cite{Clarke2012}. Here we evaluate three state-of-the-art model checkers to formally verifying PV designs w.r.t. user requirements.

@@

checking. In order to experiment with the trade-off, and in order to be able to set the dial between the two extreme points, Configurable Program Analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. %Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}. %CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing. For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs. \textcolor{red}{It is unclear what a CPA is.}

@@

The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.
